### 2016-06-29 testbed.tex
updated testbed

There are a few commands to be performed before actually changing root into the
root partion of the image.
First, to get internet access from within the Raspbian lite image it is needed
to copy our \texttt{resolv.conf} into the filesystem. Line 1 steps into Raspbian lite's
root filesystem. Then line 2 copies resolv.conf.

@@

Now, because of the ARM architecture, it is also required to copy
/usr/bin/qemu-arm-static into the image before we can continue:

@@

The final preparation before chaning root is to populate the directories proc,
sys, and dev:

@@

Finally, the filesystem is ready for us to change root. This can be done with
"proot". It may be required to install proot:

@@

Most available online material uses the more known chroot command as written in
the code block below. This did not work correctly in our machines, but we show
it as an alternative in case proot may not work on other systems.

@@

If everything went well, we should now be standing in the Raspbian lite filesystem
under its root. Optionally, we can change the prompt title to indicate that we
are chrooted:

@@

The Raspbian lite system should now be possible to use as if it had been booted
in a \ac{Raspi}. The only difference is that the laptop that we are using is
significantly faster than a \ac{Raspi}. Thus enabling us to for example update,
upgrade, and install software packages:

@@

Lets install some useful applications:
% Install packages
\begin{lstlisting}[]
(chroot) # apt-get install vim git screen
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

All the changes that are made here will exists in all \ac{Raspi}s when the
image is written to a memory card.

>>>>

There are a few commands to be performed before actually changing root into the
root partion of the image.
First, to get internet access from within the Raspbian lite image it is needed
to copy our \texttt{resolv.conf} into the filesystem. Line 1 change directory
into root filesystem of the image. The second line copies \texttt{resolv.conf}
from the testbed administrators \ac{PC} to the image.

@@

Now, because of the \ac{ARM} architecture,
\texttt{/usr/bin/qemu-arm-static} needs to be copied into the image before continuing:

@@

The final preparation before changing root is to populate the directories \texttt{proc},
\texttt{sys}, and \texttt{dev}:

@@

Finally, it is time to change root.
%Finally, the filesystem is ready for us to change root.
This can be done with \texttt{proot}. It may be required to install \texttt{proot}
using "\texttt{apt-get install proot}":

@@

Most available material online uses the more known \texttt{chroot} command as
written in the code block below instead of \texttt{proot}. This did not work
correctly in our machines, but we present the command as an alternative to
\texttt{proot} in case the testbed administrator should be in the opposite
situration where \texttt{proot} is not working.

@@

If everything went well, we should now be \texttt{chrooted} into the Raspbian lite
filesystem under its root. Optionally, change the prompt title to indicate that it
is a \texttt{chrooted} environment:

@@

The Raspbian lite system image should now be possible to use almost as if it
had been booted in a \ac{Raspi}.
A major difference is that the testbed administrator's \ac{PC} is likely
significantly faster than a \ac{Raspi}.
%The only difference is that the laptop that we are using is
%significantly faster than a \ac{Raspi}.
Thus enabling updates, upgrades, and installing new software packages much
faster than in the \ac{Raspi}s.
%Thus enabling us to for example update,
%upgrade, and install software packages:

@@

We also install a few packages that we find useful:
%Lets install some useful applications:
% Install packages
\begin{lstlisting}[]
(chroot) # apt-get install vim git screen
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

When writing the image to a memory card, all these change that has been made
to the image so far will exists in all \ac{Raspi}s.
%All the changes that are made here will exists in all \ac{Raspi}s when the
%image is written to a memory card.
